Near Optimal Behavior via Approximate State Abstraction

### 2016-02-05 paper/theory_results.tex
More widow line

We consider approximate abstractions derived from a multinomial distribution over $Q^*$ for similar reasons to our motivation in considering the Boltzmann distribution. Additionally, the multinomial distribution is appealing due to its simplicity.
\bdefn{$\epMu$}
We let $\epMu$ define a type of abstraction that, for fixed $\varepsilon$, satisfies
\begin{multline}
\epMu(s_1) = \epMu(s_2) \rightarrow \\
\forall_{a} \left|\frac{Q_G(s_1,a)}{\sum_b Q_G(s_1,b)} - \frac{Q_G(s_1,a)}{\sum_b Q_G(s_1,b)}\right| \leq \varepsilon.
\end{multline}
\edefn

>>>>

We consider approximate abstractions derived from a multinomial distribution over $Q^*$ for similar reasons to the Boltzmann distribution. Additionally, the multinomial distribution is appealing for its simplicity.
\bdefn{$\epMu$}
We let $\epMu$ define a type of abstraction that, for fixed $\varepsilon$, satisfies
\begin{multline}
\epMu(s_1) = \epMu(s_2) \rightarrow \\
\forall_{a} \left|\frac{Q_G(s_1,a)}{\sum_b Q_G(s_1,b)} - \frac{Q_G(s_1,a)}{\sum_b Q_G(s_1,b)}\right| \leq \varepsilon.
\end{multline}
\edefn
